### 2022-03-25 paper/localpsf.tex
minor changes

Let $\febasis_1, \febasis_2, \dots, \febasis_\fedim$ be a set of continuous Galerkin finite element basis functions used to discretize the problem on a mesh with mesh size parameter $h$, let $V_h := \Span\left(\febasis_1, \febasis_2, \dots, \febasis_\fedim\right)$ be the corresponding finite element space under the $L^2$ inner product, and let $p_i \in \mathbb{R}^\gdim$, $i=1,\dots, \fedim$ be the Lagrange nodes associated with the functions $\febasis_i$. We assume that the finite element basis satisfies the Kronecker property, i.e., $\febasis_i(p_i)=1$ and $\febasis_i(p_j)=0$ if $i\neq j$. 
For $u_h \in V_h \subset L^2(\Omega)$ we write $\bm{u} \in \mathbb{R}^N_\mathbf{M}$ to denote the coefficient vector for $u_h$ with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$, i.e.,
\begin{equation}
\label{eq:fem_coeff_basis}
u_h(x) = \sum_{i=1}^\fedim \bm{u}_i \febasis_i(x).
\end{equation}
Linear functionals $\rho_h \in V_h' \supset L^2(\Omega)'$ have coefficient dual vectors $\boldsymbol{\rho}\in \mathbb{R}^N_{\mathbf{M}^{-1}}$, with entries 
\begin{equation*}
\boldsymbol{\rho}_i = \rho_h(\febasis_i), \qquad i=1,\dots,N. 
\end{equation*}
Here $\bm{M} \in \mathbb{R}^{\fedim \times \fedim}$ denotes the sparse finite element mass matrix which has entries
\begin{equation*}
\bm{M}_{ij}=\int_\Omega \febasis_i(x) \febasis_j(x) dx, \qquad i,j=1,\dots,N,
\end{equation*}
the space $\mathbb{R}^N_\mathbf{M}$ is $\mathbb{R}^N$ with the inner product $(\mathbf{u},\mathbf{v})_\mathbf{M} := \mathbf{u}^T \mathbf{M} \mathbf{v}$, and $\mathbb{R}^N_{\mathbf{M}^{-1}}$ is the analogous space with $\mathbf{M}^{-1}$ replacing $\mathbf{M}$. Direct calculation shows that $\mathbf{R}^N_\mathbf{M}$ and $\mathbf{R}^N_{\mathbf{M}^{-1}}$ are isomorphic to $V_h$ and $V_h'$ as Hilbert spaces, respectively.
%, in the sense that $\left(u_h, v_h\right)_{L^2(\Omega)} = \left(\mathbf{u}, \mathbf{v}\right)_\mathbf{M}$, $\left(\rho_h, \nu_h\right)_{L^2(\Omega)} = \left(\boldsymbol{\rho}, \boldsymbol{\nu}\right)_{\mathbf{M}^{-1}}$, and $\rho_h(u) = \boldsymbol{\rho}^T\mathbf{u}$, for $u_h,v_h \in V_h$ and $\rho_h, \nu_h \in V_h'$.

>>>>

Let $\febasis_1, \febasis_2, \dots, \febasis_\fedim$ be a set of continuous Galerkin finite element basis functions used to discretize the problem on a mesh with mesh size parameter $h$, let $V_h := \Span\left(\febasis_1, \febasis_2, \dots, \febasis_\fedim\right)$ be the corresponding finite element space under the $L^2$ inner product, and let $p_i \in \mathbb{R}^\gdim$, $i=1,\dots, \fedim$ be the Lagrange nodes associated with the functions $\febasis_i$. We assume that the finite element basis satisfies the Kronecker property, i.e., $\febasis_i(p_i)=1$ and $\febasis_i(p_j)=0$ if $i\neq j$. 
For $u_h \in V_h$ we write $\bm{u} \in \mathbb{R}^N_\mathbf{M}$ to denote the coefficient vector for $u_h$ with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$, i.e.,
\begin{equation}
\label{eq:fem_coeff_basis}
u_h(x) = \sum_{i=1}^\fedim \bm{u}_i \febasis_i(x).
\end{equation}
Linear functionals $\rho_h \in V_h'$ have coefficient dual vectors $\boldsymbol{\rho}\in \mathbb{R}^N_{\mathbf{M}^{-1}}$, with entries 
\begin{equation*}
\boldsymbol{\rho}_i = \rho_h(\febasis_i), \qquad i=1,\dots,N. 
\end{equation*}
Here $\bm{M} \in \mathbb{R}^{\fedim \times \fedim}$ denotes the sparse finite element mass matrix which has entries
\begin{equation*}
\bm{M}_{ij}=\int_\Omega \febasis_i(x) \febasis_j(x) dx, \qquad i,j=1,\dots,N,
\end{equation*}
the space $\mathbb{R}^N_\mathbf{M}$ is $\mathbb{R}^N$ with the inner product $(\mathbf{u},\mathbf{v})_\mathbf{M} := \mathbf{u}^T \mathbf{M} \mathbf{v}$, and $\mathbb{R}^N_{\mathbf{M}^{-1}}$ is the analogous space with $\mathbf{M}^{-1}$ replacing $\mathbf{M}$. Direct calculation shows that $\mathbf{R}^N_\mathbf{M}$ and $\mathbf{R}^N_{\mathbf{M}^{-1}}$ are isomorphic to $V_h$ and $V_h'$ as Hilbert spaces, respectively.
%, in the sense that $\left(u_h, v_h\right)_{L^2(\Omega)} = \left(\mathbf{u}, \mathbf{v}\right)_\mathbf{M}$, $\left(\rho_h, \nu_h\right)_{L^2(\Omega)} = \left(\boldsymbol{\rho}, \boldsymbol{\nu}\right)_{\mathbf{M}^{-1}}$, and $\rho_h(u) = \boldsymbol{\rho}^T\mathbf{u}$, for $u_h,v_h \in V_h$ and $\rho_h, \nu_h \in V_h'$.
